Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-11 R0V0.tex
Start to work on ADMM

@@

\todo[inline]{Waiting for quality check of the definition of the sets $\mathscr{K}$ and $\Xi$.}

@@

In all cases, the computed matrix $W$ has a block-diagonal structure as follows
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),
\end{equation*}
the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.

In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}

@@

The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.32,1.7\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
\begin{equation*}
	Y_{ij}(q_i,\breve{q}_i)=-3.3y_i-0.09x_iy_i
\end{equation*}
for pair of indexes $(i,j)$ given as $(1,1)$, $(2,3)$, $(3,5)$ and $(4,6)$. Also, 
\begin{align*}
	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\\	
	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\\	
	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\\	
	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)
\end{align*}

@@

In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(i)=\{i\}$, 
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\{e_1\},&\mathbf{C}_3=\mathbf{C}_4=\{e_2\},\\
		\mathbf{C}_5=\mathbf{C}_6=\{e_3\},&\mathbf{C}_7=\mathbf{C}_8=\{e_4\}
	\end{array}
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
 Y=&\mathbin{\mathtt{diag}}\left(Y_1,Y_2,Y_3,Y_4\right)
\end{align*}
where
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and, for each index $i=1,4$,
\begin{align*}
 Y_i(q_i)=[-3.1y_i+0.06x_iy_i,-3.6-0.02x_i-2.3y_i^2-2.4x_i^2]
\end{align*}
and, for each index $i=2,3$,
\begin{align*}
 Y_i(q_i)=[-3.1y_i,-3.8-2.1y_i^2-2.2x_i^2].
\end{align*}

>>>>

The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in parallel \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this framework, define the sets $\mathbf{Y}^n=\{Y\in\mathbb{R}^{m\times n}\}$, $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{(W_1,\ldots,W_N,Y)\in \mathbb{R}^{n_i\times n_i}\times \mathbb{R}^{m\times n}:\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),T\prec0\}$. For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
\begin{equation*}
	H(\mathbf{G},g)=\begin{cases}
									0,&g\in \mathbf{G}\\
									\infty,&\text{Otherwise.}
								\end{cases}
\end{equation*}

The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
\begin{equation*}
	\begin{array}{rl}
		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N,Z_{N+1}))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
		\text{subject to}&W_i-Z_i=0,\quad \forall i\in\mathbb{N}_{[1,N]}\\
		&Y-Z_{N+1}=0
	\end{array}
\end{equation*}

@@

@@

In all cases, the computed matrix $W$ has a block-diagonal structure as follows
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right)\;.
\end{equation*}
the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.

In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\;,\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2\;.
\end{align*}

@@

The time taken by the parser to solve the MI \eqref{eq:MI formulation}, in this case, was 3.5 seconds. The components of the matrix $W$ and the matrix $Y$ that form a solution to the \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.32,1.7\right)\quad\text{and}\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:neighbor} with elements
\begin{equation*}
	Y_{ij}(q_i,\breve{q}_i)=-3.3y_i-0.09x_iy_i
\end{equation*}
for pair of indexes $(i,j)$ given as $(1,1)$, $(2,3)$, $(3,5)$ and $(4,6)$. Also, 
\begin{align*}
	Y_{12}(q_1,\breve{q}_1)=&-2.8-0.01x_1-2(y_1^2+y_2^2+x_1^2+x_2^2)\;,\\	
	Y_{24}(q_2,\breve{q}_2)=&-3-2(y_1^2+y_2^2+y_3^2+x_1^2+x_2^2+x_3^2)\;,\\	
	Y_{36}(q_3,\breve{q}_3)=&-3-2(y_2^2+y_3^2+y_4^2+x_2^2+x_3^2+x_4^2)\;,\\	
	Y_{48}(q_4,\breve{q}_4)=&-2.5-0.01x_4-1.5(y_3^2+y_4^2+x_3^2+x_4^2)\;.
\end{align*}

@@

In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(k)=\{k\}$ and $\mathbf{X}(\mathscr{K}(k))=\{q_k\}$, where $k\in\mathbb{N}_{[1,4]}$. Moreover, 
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\left\{\begin{bmatrix}1,0,0,0\end{bmatrix}^\top\right\},&\mathbf{C}_3=\mathbf{C}_4=\left\{\begin{bmatrix}0,1,0,0\end{bmatrix}^\top\right\},\\
		\mathbf{C}_5=\mathbf{C}_6=\left\{\begin{bmatrix}0,0,1,0\end{bmatrix}^\top\right\},&\mathbf{C}_7=\mathbf{C}_8=\left\{\begin{bmatrix}0,0,0,1\end{bmatrix}^\top\right\}\;.
	\end{array}
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
 Y=&\begin{bmatrix}
 	Y_{11}&Y_{12}&0&0&0&0&0&0\\
 	0&0&Y_{23}&Y_{24}&0&0&0&0\\
 	0&0&0&0&Y_{35}&Y_{36}&0&0\\
 	0&0&0&0&0&0&Y_{47}&Y_{48}
 \end{bmatrix}
\end{align*}
where
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and
\begin{align*}
 Y_{11}(q_i)=Y_{47}(q_i)=&\ -3.1y_i+0.06x_iy_i\;,\\
 Y_{12}(q_i)=Y_{48}(q_i)=&\ -3.6-0.02x_i-2.3y_i^2-2.4x_i^2\;,\\
 Y_{23}(q_i)=Y_{35}(q_i)=&\ -3.1y_i\;,\\
 Y_{24}(q_i)=Y_{26}(q_i)=&\ -3.8-2.1y_i^2-2.2x_i^2\;.
\end{align*}
